Single-step Hybrid Predition

### 2016-12-09 reports/transformed_kernel_predictions.Rmd
Init plots for transformed kernel predictions

```{r Load-LOOCV-Data, cache = TRUE}
log_file <- fread("./data/derived/pred_log.txt")

pred_df <- log_file %>%
  .$Job_ID %>%
  as.list() %>%
  map(~readRDS(paste0("./data/derived/predictions/", ., ".RDS"))) %>%
  bind_rows(.id = "id") %>%
  left_join(y = log_file %>% select(Job_ID, Pred1, Pred2, Pred3, Trait, Iter),
            by = "Job_ID") %>%
  filter(Iter == 30000) %>%
  unite(col = Predictor, Pred1, Pred2, Pred3, sep = "-") %>%
  mutate(Trait = fct_recode(Trait,
    "DMY" = "GTM",
    "DMC" = "GTS",
    "FAT" = "FETT",
    "PRO" = "RPR",
    "SUG" = "XZ"
  )) %>%
  mutate(Trait = fct_relevel(Trait,
                             "DMY", "DMC", "ADF", "FAT", "PRO", "STA", "SUG"),
         Predictor = as.factor(Predictor)) %>%
  select(-Job_ID, -Iter)

# Update the variable 'Trait' for subsequent joins with 'pred_df'.
log_file <- log_file %>%
  filter(Iter == 30000) %>%
  mutate(Trait = fct_recode(Trait,
    "DMY" = "GTM",
    "DMC" = "GTS",
    "FAT" = "FETT",
    "PRO" = "RPR",
    "SUG" = "XZ"
  )) %>%
  mutate(Trait = fct_relevel(Trait,
                             "DMY", "DMC", "ADF", "FAT", "PRO",
                             "STA", "SUG")) %>%
  unite(col = Predictor, Pred1, Pred2, Pred3, sep = "-")
```

## Distribution of predicted and observed values
```{r Distribution-y-yhat, cache = TRUE, fig.height = 12, fig.cap = "Frequency polygon of observed and predicted values for seven agronomic traits (columns) and nine sets of predictors (rows)."}
# Specify a unified predictor order.
pred_order <- c("ped42-none-none", "snp42-none-none", "mrna42-none-none",
                "ped100-none-none", "snp100-none-none", "ped100-snp77-none",
                "ped100-mrna42-none", "snp100-mrna42-none",
                "ped100-snp77-mrna42")
legend_labs <- expression(y, hat(y))
pred_df %>%
  filter(Predictor != "snp77-none-none") %>%
  gather(key = Value, value = `Phenotypic Value`, y, yhat) %>%
  mutate(Predictor = fct_relevel(Predictor, pred_order)) %>%
  ggplot(aes(x = `Phenotypic Value`, color = Value)) +
  geom_freqpoly() +
  scale_color_manual(values = c("#1f78b4", "#e31a1c"), labels = legend_labs) +
  facet_grid(Predictor ~ Trait, scales = "free") +
  theme_bw() +
  theme(legend.position = "top",
        strip.text.y = element_text(size = 7)) +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  ylab("Frequency")
```

@@

overview_df <- pred_df %>%
  group_by(Predictor, Trait) %>%
  summarize(r = cor(y, yhat)) %>%
  ungroup() %>%
  as.data.frame() %>%
  left_join(y = cv_df, by = c("Predictor", "Trait")) %>%
  as_tibble() %>%
  mutate(Predictor = as.factor(Predictor),
         Predictor = forcats::fct_reorder(Predictor, CV),
         Trait = fct_relevel(Trait,
                             "DMY", "DMC", "ADF", "FAT", "PRO",
                             "STA", "SUG"),
         Group = ifelse(Predictor %in% c("snp42-none-none",
                                         "ped42-none-none",
                                         "mrna42-none-none"),
                        yes = "Reduced", no = "Full")
  ) %>%
  mutate(Group = as.factor(Group))
```

>>>>

```{r Load-LOOCV-Data, cache = TRUE}
log_file <- fread("./data/derived/pred_log.txt")
ped_log <- log_file %>%
  filter(Pred1 %in% c("ped100", "ped77", "ped42"),
         Pred2 == "none",
         Pred3 == "none")
log_file %>%
  filter(Transformation == TRUE)
trait_order <- levels(log_file$Trait)
log_file <- log_file %>%
  select(-Trait) %>%
  distinct()

pred_lst <- lapply(seq_len(nrow(log_file)), FUN = function(i) {
  job_id <- log_file[i, Job_ID, ]
  pred_obj <- readRDS(paste0("./data/derived/predictions/", job_id, ".RDS"))
  geno_number <- pred_obj %>%
    .$Geno %>%
    unique() %>%
    length()
  geno_trait_labels <- rep(trait_order, times = geno_number)
  pred_obj$Trait <- geno_trait_labels
  pred_obj$Predictor <- log_file[i, Predictor, ]
  pred_obj 
})

pred_df <- pred_lst %>%
  bind_rows() %>% 
  mutate(Trait = as.factor(Trait)) %>%
  mutate(Trait = fct_relevel(Trait,
                             "DMY", "DMC", "ADF", "FAT", "PRO", "STA", "SUG"),
         Predictor = as.factor(Predictor))
```

## Distribution of predicted and observed values
```{r Distribution-y-yhat, cache = TRUE, fig.height = 12, fig.cap = "Frequency polygon of observed and predicted values for seven agronomic traits (columns) and nine sets of predictors (rows)."}
# Specify a unified predictor order.
pred_order <- c("snp42-none-none", "mrna42-none-none",
                "snp100-none-none", "ped100-snp77-none",
                "ped100-mrna42-none", "snp100-mrna42-none",
                "ped100-snp77-mrna42")
legend_labs <- expression(y, hat(y))
pred_df %>%
  filter(Predictor != "snp77-none-none") %>%
  gather(key = Value, value = `Phenotypic Value`, y, yhat) %>%
  mutate(Predictor = fct_relevel(Predictor, pred_order),
         Value = as.factor(Value)) %>%
  ggplot(aes(x = `Phenotypic Value`, color = Value)) +
  geom_freqpoly() +
  scale_color_manual(values = c("#1f78b4", "#e31a1c"), labels = legend_labs) +
  facet_grid(Predictor ~ Trait, scales = "free") +
  theme_bw() +
  theme(legend.position = "top",
        strip.text.y = element_text(size = 7)) +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  ylab("Frequency")
```

@@

overview_df <- pred_df %>%
  group_by(Predictor, Trait) %>%
  summarize(r = cor(y, yhat)) %>%
  ungroup() %>%
  as.data.frame() %>%
  left_join(y = cv_df, by = c("Predictor", "Trait")) %>%
  as_tibble() %>%
  mutate(Predictor = as.factor(Predictor),
         Predictor = forcats::fct_reorder(Predictor, CV),
         Trait = fct_relevel(Trait,
                             "DMY", "DMC", "ADF", "FAT", "PRO",
                             "STA", "SUG"),
         Group = ifelse(Predictor %in% c("snp42-none-none",
                                         "mrna42-none-none"),
                        yes = "Reduced", no = "Full")
  ) %>%
  mutate(Group = as.factor(Group))
```
